Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake

### 2016-07-07 JGRRevision/2016JB013114.tex
removed tiny ellipses in S4 and fixed the bib

\documentclass[draft,linenumbers]{AGUJournal}
\draftfalse
\usepackage{amssymb,amsmath,amsthm,amsfonts}
%% For final version.
% \documentclass{AGUJournal}

\journalname{JGR-Solid Earth}

\begin{document}

\title{Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake}

\authors{T. T. Hines\affil{1}, E. A. Hetland\affil{1}}

\affiliation{1}{Department of Earth and Environmental Sciences, University of Michigan, Ann Arbor, Michigan, USA.}

\correspondingauthor{T. T. Hines}{hinest@umich.edu}

%% Keypoints, final entry on title page.

% Example: 
% \begin{keypoints}
% \item	List up to three key points (at least one is required)
% \item	Key Points summarize the main points and conclusions of the article
% \item	Each must be 100 characters or less with no special characters or punctuation 
% \end{keypoints}

%  List up to three key points (at least one is required)
%  Key Points summarize the main points and conclusions of the article
%  Each must be 100 characters or less with no special characters or punctuation

\begin{keypoints}
\item Transient postseismic deformation can be observed following the El Mayor-Cucapah earthquake at epicentral distances of up to 400 km

\item Near-field postseismic deformation exhibits early transience that decays to a sustained rate which is elevated above the preseismic trend

\item Far-field postseismic deformation can be explained with a Zener or Burgers rheology upper mantle

\end{keypoints}

@@

\begin{table}\label{tab:MaterialProperties}
\begin{tabular} {l l l l l}
depth (km) &$\lambda$ (GPa)&$\mu$ (GPa)&$\eta_\mathrm{eff}$ ($10^{18}$ Pa s) & $\mu_\mathrm{k}/\mu$\\ \hline
0-5 & 24.0 & 24.0 & - & -\\
5-15 & 35.0 & 35.0 & - & -\\
15-30 & 42.0 & 42.0 & 44.3 & 0.0\\
30-60 & 61.0 & 61.0 & 5.91 & 0.375\\
60-90 & 61.0 & 61.0 & 1.99 & 0.375\\
90-120 & 61.0 & 61.0 & 1.31 & 0.375\\
120-150 & 61.0 & 61.0 & 1.10 & 0.375\\
150-$\infty$ & 61.0 & 61.0 & 1.07 & 0.375\\
\end{tabular}
\caption{Assumed and estimated material properties. $\lambda$ and $\mu$ are assumed known \textit{a priori} and are based on the values used for the coseismic model by \citet{Wei2011}.  The values for $\eta_\mathrm{eff}$ are estimated in Section \ref{sec:InitialInversion}, and $\frac{\mu_k}{\mu}$ are the optimal shear moduli ratios found in Section \ref{sec:FullInversion} for a Zener rheology upper mantle.}

\end{table}
We seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah earthquake and we consider afterslip and viscoelastic relaxation as candidate mechanisms.  Poroelastic rebound has also been used to model postseismic deformation \citep[e.g.][]{Jonsson2003}; however, \citet{Gonzalez-ortega2014} found that poroelastic rebound is unlikely to be a significant contributor to postseismic deformation following the El Mayor-Cucapah earthquake. Furthermore, we consider stations which are sufficiently far away from the rupture that poroelastic rebound should be insignificant.

@@

\subsection{Full Postseismic Inversion}\label{sec:FullInversion}

In the previous section, we used the inverse method from \citet{Hines2016} to constrain the effective viscosity structure required to explain the first 0.8 years of postseismic deformation. In this section, we use these effective viscosities as a prior constraint when searching for models which are capable of describing the available five years of postseismic data, where our forward problem is now eq. (\ref{GeneralForward}) rather than the approximation given by eq. (\ref{ApproxForward}).  We perform a series of fault slip inversions assuming a variety of rheologies for the lower crust and upper mantle which are consistent with our findings from Section \ref{sec:InitialInversion}.  We appraise each model using the mean chi-squared value,

@@

\section{Discussion}\label{Discussion}

It has long been recognized that deep afterslip and viscoelastic relaxation following an upper crustal earthquake can result in similar horizontal ground deformation at the surface \citep[e.g.][]{Savage1990, Pollitz2001, Hearn2003, Feigl2006}. The similarity of the horizontal postseismic deformation results in a non-uniqueness in inferences of afterslip or viscoelastic relaxation.  The spatial pattern of vertical postseismic deformation has been proposed to be a discriminant between deep afterslip and viscoelastic relaxation \citep[e.g.][]{Pollitz2001, Hearn2003}. It is, however, important to note that patterns of vertical deformation are very sensitive to the depth-dependence of viscosity below the upper crust \citep{Yang1981,Hetland2014}.  The similarity between deformation resulting from deep afterslip and viscoelastic relaxation of coseismic stresses is different from the ill-posedness described in Section \ref{sec:InitialInversion}. In our method, any inferred afterslip will also mechanically drive additional viscoelastic relaxation.  The horizontal deformation resulting from deep afterslip will generally be in the opposite direction as horizontal deformation resulting from viscoelastic relaxation of subsequent stresses in the lower crust (Figure \ref{fig:LowerCrust}).  As a result, there is a trade-off between inferences of deep afterslip and lower crustal viscosity.  In our synthetic tests in \citet{Hines2016}, we have found that inverting surface deformation for afterslip and viscosity within the same depth interval tends to result in overestimated afterslip and an underestimated viscosity.

@@

\section{Conclusion}

We have extracted a smoothed estimate of postseismic deformation following the El Mayor-Cucapah earthquake from GPS displacement time series.  Our estimated postseismic deformation reveals far-field (epicentral distances ${\gtrsim}200$ km) transient deformation which is undetectable after about three years. Near-field deformation exhibits transience that decays to a sustained, elevated rate after about one or two years.  We found that near-field transient deformation can be explained with shallow afterslip, and the sustained rate of near-field deformation can either be explained with continued afterslip or viscoelastic relaxation in the lower crust.  Far-field transient deformation can be more definitively ascribed to viscoelastic relaxation at depths greater than ${\sim}60$ km. Beneath that depth, a transient viscosity of ${\sim}1\times10^{18}$ Pa s is required to describe the rate of far-field deformation throughout the five years considered in this study.  By describing the available postseismic deformation with a transient rheology in the mantle, our preferred model does not conflict with the generally higher steady-state viscosities inferred from geophysical processes occurring over longer time scales.

@@

\bibitem[{\textit{Argus et~al.}(2005)\textit{Argus, Heflin, Peltzer,
  Cramp{\'{e}}, and Webb}}]{Argus2005}
Argus, D.~F., M.~B. Heflin, G.~Peltzer, F.~Cramp{\'{e}}, and F.~H. Webb (2005),
  {Interseismic strain accumulation and anthropogenic motion in metropolitan
  Los Angeles}, \textit{Journal of Geophysical Research: Solid Earth},
  \textit{110}(4), 1--26, \doi{10.1029/2003JB002934}.

@@

\bibitem[{\textit{Bawden et~al.}(2001)\textit{Bawden, Thatcher, Stein, Hudnut,
  and Peltzer}}]{Bawden2001}
Bawden, G.~W., W.~Thatcher, R.~S. Stein, K.~W. Hudnut, and G.~Peltzer (2001),
  {Tectonic contraction across Los Angeles after removal of groundwater pumping
  effects.}, \textit{Nature}, \textit{412}(August), 812--815,
  \doi{10.1038/35090558}.

\bibitem[{\textit{Bills and May}(1987)}]{Bills1987}
Bills, B.~G., and G.~M. May (1987), {Lake Bonneville: Constraints on
  Lithospheric Thickness and Upper Mantle Viscosity From Isostatic Warping of
  Bonneville, Provo, and Gilbert Stage Shorelines}, \textit{Journal of
  Geophysical Research-Solid Earth and Planets}, \textit{92}(B11),
  11,493--11,508, \doi{10.1029/JB092iB11p11493}.

@@

\bibitem[{\textit{Cavali{\'{e}} et~al.}(2007)\textit{Cavali{\'{e}}, Doin,
  Lasserre, and Briole}}]{Cavalie2007}
Cavali{\'{e}}, O., M.~P. Doin, C.~Lasserre, and P.~Briole (2007), {Ground
  motion measurement in the Lake Mead area, Nevada, by differential synthetic
  aperture radar interferometry time series analysis: Probing the lithosphere
  rheological structure}, \textit{Journal of Geophysical Research: Solid
  Earth}, \textit{112}(3), 1--18, \doi{10.1029/2006JB004344}.

\bibitem[{\textit{Cetin et~al.}(2014)\textit{Cetin, Cakir, Meghraoui, Ergintav,
  and Akoglu}}]{Cetin2014}
Cetin, E., Z.~Cakir, M.~Meghraoui, S.~Ergintav, and A.~M. Akoglu (2014),
  {Extent and distribution of aseismic slip on the Ismetpasa segment of the
  North Anatolian Fault (Turkey) from Persistent Scatterer InSAR},
  \textit{Geochemistry, Geophysics, Geosystems}, \textit{15},
  \doi{10.1002/2014GC005307.Received}.

@@

\bibitem[{\textit{Crittenden}(1967)}]{Crittenden1967}
Crittenden, M. (1967), {Viscosity and Finite Strength of the Mantle as
  Determined from Water and Ice Loads*}, \textit{Geophysical Journal of the
  Royal Astronomical {\ldots}}, pp. 261--279,
  \doi{10.1111/j.1365-246X.1967.tb06243.x}.

\bibitem[{\textit{Davis et~al.}(2012)\textit{Davis, Wernicke, and
  Tamisiea}}]{Davis2012}
Davis, J.~L., B.~P. Wernicke, and M.~E. Tamisiea (2012), {On seasonal signals
  in geodetic time series}, \textit{Journal of Geophysical Research: Solid
  Earth}, \textit{117}(1), 1--10, \doi{10.1029/2011JB008690}.

@@

\bibitem[{\textit{Freed et~al.}(2006)\textit{Freed, B{\"{u}}rgmann, Calais,
  Freymueller, and Hreinsd{\'{o}}ttir}}]{Freed2006a}
Freed, A.~M., R.~B{\"{u}}rgmann, E.~Calais, J.~Freymueller, and
  S.~Hreinsd{\'{o}}ttir (2006), {Implications of deformation following the 2002
  Denali, Alaska, earthquake for postseismic relaxation processes and
  lithospheric rheology}, \textit{Journal of Geophysical Research: Solid
  Earth}, \textit{111}, 1--23, \doi{10.1029/2005JB003894}.

\bibitem[{\textit{Freed et~al.}(2007)\textit{Freed, B{\"{u}}rgmann, and
  Herring}}]{Freed2007a}
Freed, A.~M., R.~B{\"{u}}rgmann, and T.~Herring (2007), {Far-reaching transient
  motions after Mojave earthquakes require broad mantle flow beneath a strong
  crust}, \textit{Geophysical Research Letters}, \textit{34}, 1--5,
  \doi{10.1029/2007GL030959}.

\bibitem[{\textit{Gonzalez-Ortega et~al.}(2014)\textit{Gonzalez-Ortega, Fialko,
  Sandwell, Nava-pichardo, Fletcher, Gonzalez-garcia, Lipovsky, Floyd, and
  Funning}}]{Gonzalez-ortega2014}
Gonzalez-Ortega, A., Y.~Fialko, D.~Sandwell, F.~A. Nava-pichardo, J.~Fletcher,
  J.~Gonzalez-garcia, B.~Lipovsky, M.~Floyd, and G.~Funning (2014), {El
  Mayor-Cucapah (Mw7.2) earthquake: early near-field postseismic deformation
  from InSar and GPS observations}, \textit{Journal of Geophysical Research},
  \textit{119}, 1482--1497, \doi{10.1002/2013JB010193.Received}.

\bibitem[{\textit{Hauksson et~al.}(2011)\textit{Hauksson, Stock, Hutton, Yang,
  Vidal-Villegas, and Kanamori}}]{Hauksson2011}
Hauksson, E., J.~Stock, K.~Hutton, W.~Yang, J.~A. Vidal-Villegas, and
  H.~Kanamori (2011), {The 2010 Mw 7.2 El mayor-cucapah earthquake sequence,
  Baja California, Mexico and Southernmost California, USA: Active
  seismotectonics along the Mexican pacific margin}, \textit{Pure and Applied
  Geophysics}, \textit{168}(3918), 1255--1277, \doi{10.1007/s00024-010-0209-7}.

\bibitem[{\textit{Hearn}(2003)}]{Hearn2003}
Hearn, E.~H. (2003), {What can GPS data tell us about the dynamics of
  post-seismic deformation ?}, (2003), 753--777.

\bibitem[{\textit{Hearn et~al.}(2009)\textit{Hearn, McClusky, Ergintav, and
  Reilinger}}]{Hearn2009}
Hearn, E.~H., S.~McClusky, S.~Ergintav, and R.~E. Reilinger (2009), {Izmit
  earthquake postseismic deformation and dynamics of the North Anatolian Fault
  Zone}, \textit{Journal of Geophysical Research: Solid Earth},
  \textit{114}(August 2008), 1--21, \doi{10.1029/2008JB006026}.

\bibitem[{\textit{Hetland}(2003)}]{Hetland2003}
Hetland, E.~A. (2003), {Postseismic relaxation across the Central Nevada
  Seismic Belt}, \textit{Journal of Geophysical Research}, \textit{108}(Figure
  2), 1--13, \doi{10.1029/2002JB002257}.

\bibitem[{\textit{Hetland and Zhang}(2014)}]{Hetland2014}
Hetland, E.~A., and G.~Zhang (2014), {Effect of shear zones on post-seismic
  deformation with application to the 1997 Mw 7.6 manyi earthquake},
  \textit{Geophysical Journal International}, \textit{198}, 259--269,
  \doi{10.1093/gji/ggu127}.

@@

\bibitem[{\textit{Jacobs et~al.}(2002)\textit{Jacobs, Sandwell, Fialko, and
  Sichoix}}]{Jacobs2002}
Jacobs, A., D.~Sandwell, Y.~Fialko, and L.~Sichoix (2002), {The 1999 (Mw7.1)
  Hector Mine, California, Earthquake: Near-Field Postseismic Deformation from
  ERS Interferometry}, \textit{Bulletin of the Seismological Society of
  America}, \textit{92}(May), 1433--1442.

\bibitem[{\textit{Johnson and Segall}(2004)}]{Johnson2004}
Johnson, K.~M., and P.~Segall (2004), {Viscoelastic earthquake cycle models
  with deep stress-driven creep along the San Andreas fault system},
  \textit{Journal of Geophysical Research: Solid Earth}, \textit{109}, 1--19,
  \doi{10.1029/2004JB003096}.

@@

\bibitem[{\textit{J{\'{o}}nsson et~al.}(2003)\textit{J{\'{o}}nsson, Segall,
  Pedersen, and Bjornsson}}]{Jonsson2003}
J{\'{o}}nsson, S., P.~Segall, R.~Pedersen, and G.~Bjornsson (2003),
  {Post-earthquake ground movements correlated to pore-pressure transients},
  \textit{Nature}, \textit{424}(July), 179--183, \doi{10.1038/nature01758.1.}

@@

\bibitem[{\textit{Kroll et~al.}(2013)\textit{Kroll, Cochran, Richards-Dinger,
  and Sumy}}]{Kroll2013}
Kroll, K.~A., E.~S. Cochran, K.~B. Richards-Dinger, and D.~F. Sumy (2013),
  {Aftershocks of the 2010 Mw 7.2 El Mayor-Cucapah earthquake reveal complex
  faulting in the Yuha Desert, California}, \textit{Journal of Geophysical
  Research: Solid Earth}, \textit{118}(October), 6146--6164,
  \doi{10.1002/2013JB010529}.

\bibitem[{\textit{Lekic et~al.}(2011)\textit{Lekic, French, and
  Fischer}}]{Lekic2011}
Lekic, V., S.~W. French, and K.~M. Fischer (2011), {Lithospheric Thinning
  Beneath Rifted Regions of Southern California}, \textit{Science},
  \textit{334}(November), 783--787.

\bibitem[{\textit{Liu et~al.}(1976)\textit{Liu, Anderson, and
  Kanamori}}]{Liu1976}
Liu, H.-P., D.~L. Anderson, and H.~Kanamori (1976), {Velocity dispersion due to
  anelasticity; implications for seismology and mantle composition},
  \textit{Geophysical Journal International}, \textit{47}(1), 41--58,
  \doi{10.1111/j.1365-246X.1976.tb01261.x}.

\bibitem[{\textit{Lundgren et~al.}(2009)\textit{Lundgren, Hetland, Liu, and
  Fielding}}]{Lundgren2009}
Lundgren, P., E.~A. Hetland, Z.~Liu, and E.~J. Fielding (2009), {Southern San
  Andreas-San Jacinto fault system slip rates estimated from earthquake cycle
  models constrained by GPS and interferometric synthetic aperture radar
  observations}, \textit{Journal of Geophysical Research: Solid Earth},
  \textit{114}(2), 1--18, \doi{10.1029/2008JB005996}.

\bibitem[{\textit{McGuire and Segall}(2003)}]{McGuire2003}
McGuire, J.~J., and P.~Segall (2003), {Imaging of aseismic fault slip
  transients recorded by dense geodetic networks}, \textit{Geophysical Journal
  International}, \textit{155}(3), 778--788,
  \doi{10.1111/j.1365-246X.2003.02022.x}.

\bibitem[{\textit{Meade and Hager}(2005)}]{Meade2005}
Meade, B.~J., and B.~H. Hager (2005), {Block models of crustal motion in
  southern California constrained by GPS measurements}, \textit{Journal of
  Geophysical Research B: Solid Earth}, \textit{110}, 1--19,
  \doi{10.1029/2004JB003209}.

\bibitem[{\textit{Murray and Segall}(2005)}]{Murray2005}
Murray, J.~R., and P.~Segall (2005), {Spatiotemporal evolution of a transient
  slip event on the San Andreas fault near Parkfield, California},
  \textit{Journal of Geophysical Research : Solid Earth}, \textit{110}(9),
  1--12, \doi{10.1029/2005JB003651}.

@@

\bibitem[{\textit{Pollitz et~al.}(2000)\textit{Pollitz, Peltzer, and
  B{\"{u}}rgmann}}]{Pollitz2000}
Pollitz, F.~F., G.~Peltzer, and R.~B{\"{u}}rgmann (2000), {Mobility of
  continental mantle: Evidence from postseismic geodetic observations following
  the 1992 Landers earthquake}, \textit{Journal of Geophysical Research},
  \textit{105}(1999), 8035, \doi{10.1029/1999JB900380}.

>>>>

\documentclass[draft,linenumbers]{AGUJournal}
\draftfalse
\usepackage{amssymb,amsmath,amsthm,amsfonts}
%% For final version.
% \documentclass{AGUJournal}
\journalname{JGR-Solid Earth}

\begin{document}
\title{Rheologic constraints on the upper mantle from five years of postseismic deformation following the El Mayor-Cucapah earthquake}
\authors{T. T. Hines\affil{1}, E. A. Hetland\affil{1}}
\affiliation{1}{Department of Earth and Environmental Sciences, University of Michigan, Ann Arbor, Michigan, USA.}
\correspondingauthor{T. T. Hines}{hinest@umich.edu}

\begin{keypoints}
\item Transient postseismic deformation can be observed following the El Mayor-Cucapah earthquake at epicentral distances of up to 400 km
\item Near-field postseismic deformation exhibits early transience that decays to a sustained rate which is elevated above the preseismic trend 
\item Far-field postseismic deformation can be explained with a Zener or Burgers rheology upper mantle 
\end{keypoints}

@@

\begin{table}\label{tab:MaterialProperties}
\begin{tabular} {l l l l l}
depth (km) &$\lambda$ (GPa)&$\mu$ (GPa)&$\eta_\mathrm{eff}$ ($10^{18}$ Pa s) & $\mu_\mathrm{k}/\mu$\\ \hline
0-5 & 24.0 & 24.0 & - & -\\
5-15 & 35.0 & 35.0 & - & -\\
15-30 & 42.0 & 42.0 & 44.3 & 0.0\\
30-60 & 61.0 & 61.0 & 5.91 & 0.375\\
60-90 & 61.0 & 61.0 & 1.99 & 0.375\\
90-120 & 61.0 & 61.0 & 1.31 & 0.375\\
120-150 & 61.0 & 61.0 & 1.10 & 0.375\\
150-$\infty$ & 61.0 & 61.0 & 1.07 & 0.375\\
\end{tabular}
\caption{Assumed and estimated material properties. $\lambda$ and $\mu$ are assumed known \textit{a priori} and are based on the values used for the coseismic model by \citet{Wei2011}.  The values for $\eta_\mathrm{eff}$ are estimated in Section \ref{sec:InitialInversion}, and $\frac{\mu_k}{\mu}$ are the optimal shear moduli ratios found in Section \ref{sec:FullInversion} for a Zener rheology upper mantle.} 
\end{table}

We seek to find the mechanisms driving five years of postseismic deformation following the El Mayor-Cucapah earthquake and we consider afterslip and viscoelastic relaxation as candidate mechanisms.  Poroelastic rebound has also been used to model postseismic deformation \citep[e.g.][]{Jonsson2003}; however, \citet{Gonzalez-ortega2014} found that poroelastic rebound is unlikely to be a significant contributor to postseismic deformation following the El Mayor-Cucapah earthquake. Furthermore, we consider stations which are sufficiently far away from the rupture that poroelastic rebound should be insignificant.

@@

\subsection{Full Postseismic Inversion}\label{sec:FullInversion} 
In the previous section, we used the inverse method from \citet{Hines2016} to constrain the effective viscosity structure required to explain the first 0.8 years of postseismic deformation. In this section, we use these effective viscosities as a prior constraint when searching for models which are capable of describing the available five years of postseismic data, where our forward problem is now eq. (\ref{GeneralForward}) rather than the approximation given by eq. (\ref{ApproxForward}).  We perform a series of fault slip inversions assuming a variety of rheologies for the lower crust and upper mantle which are consistent with our findings from Section \ref{sec:InitialInversion}.  We appraise each model using the mean chi-squared value,

@@

\section{Discussion}\label{Discussion}
It has long been recognized that deep afterslip and viscoelastic relaxation following an upper crustal earthquake can result in similar horizontal ground deformation at the surface \citep[e.g.][]{Savage1990, Pollitz2001, Hearn2003, Feigl2006}. The similarity of the horizontal postseismic deformation results in a non-uniqueness in inferences of afterslip or viscoelastic relaxation.  The spatial pattern of vertical postseismic deformation has been proposed to be a discriminant between deep afterslip and viscoelastic relaxation \citep[e.g.][]{Pollitz2001, Hearn2003}. It is, however, important to note that patterns of vertical deformation are very sensitive to the depth-dependence of viscosity below the upper crust \citep{Yang1981,Hetland2014}.  The similarity between deformation resulting from deep afterslip and viscoelastic relaxation of coseismic stresses is different from the ill-posedness described in Section \ref{sec:InitialInversion}. In our method, any inferred afterslip will also mechanically drive additional viscoelastic relaxation.  The horizontal deformation resulting from deep afterslip will generally be in the opposite direction as horizontal deformation resulting from viscoelastic relaxation of subsequent stresses in the lower crust (Figure \ref{fig:LowerCrust}).  As a result, there is a trade-off between inferences of deep afterslip and lower crustal viscosity.  In our synthetic tests in \citet{Hines2016}, we have found that inverting surface deformation for afterslip and viscosity within the same depth interval tends to result in overestimated afterslip and an underestimated viscosity.

@@

\section{Conclusion}
We have extracted a smoothed estimate of postseismic deformation following the El Mayor-Cucapah earthquake from GPS displacement time series.  Our estimated postseismic deformation reveals far-field (epicentral distances ${\gtrsim}200$ km) transient deformation which is undetectable after about three years. Near-field deformation exhibits transience that decays to a sustained, elevated rate after about one or two years.  We found that near-field transient deformation can be explained with shallow afterslip, and the sustained rate of near-field deformation can either be explained with continued afterslip or viscoelastic relaxation in the lower crust.  Far-field transient deformation can be more definitively ascribed to viscoelastic relaxation at depths greater than ${\sim}60$ km. Beneath that depth, a transient viscosity of ${\sim}1\times10^{18}$ Pa s is required to describe the rate of far-field deformation throughout the five years considered in this study.  By describing the available postseismic deformation with a transient rheology in the mantle, our preferred model does not conflict with the generally higher steady-state viscosities inferred from geophysical processes occurring over longer time scales.

@@

\bibitem[{\textit{Argus et~al.}(2005)\textit{Argus, Heflin, Peltzer, Cramp{\'{e}}, and Webb}}]{Argus2005}
Argus, D.~F., M.~B. Heflin, G.~Peltzer, F.~Cramp{\'{e}}, and F.~H. Webb (2005), {Interseismic strain accumulation and anthropogenic motion in metropolitan Los Angeles}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{110}(B04401), 1--26, \doi{10.1029/2003JB002934}.

@@

\bibitem[{\textit{Bawden et~al.}(2001)\textit{Bawden, Thatcher, Stein, Hudnut, and Peltzer}}]{Bawden2001}
Bawden, G.~W., W.~Thatcher, R.~S. Stein, K.~W. Hudnut, and G.~Peltzer (2001), {Tectonic contraction across Los Angeles after removal of groundwater pumping effects.}, \textit{Nature}, \textit{412}, 812--815, \doi{10.1038/35090558}.

\bibitem[{\textit{Bills and May}(1987)}]{Bills1987}
Bills, B.~G., and G.~M. May (1987), {Lake Bonneville: Constraints on Lithospheric Thickness and Upper Mantle Viscosity From Isostatic Warping of Bonneville, Provo, and Gilbert Stage Shorelines}, \textit{Journal of Geophysical Research-Solid Earth and Planets}, \textit{92}(B11), 11, 11493--11508, \doi{10.1029/JB092iB11p11493}.

@@

\bibitem[{\textit{Cavali{\'{e}} et~al.}(2007)\textit{Cavali{\'{e}}, Doin, Lasserre, and Briole}}]{Cavalie2007}
Cavali{\'{e}}, O., M.~P. Doin, C.~Lasserre, and P.~Briole (2007), {Ground motion measurement in the Lake Mead area, Nevada, by differential synthetic aperture radar interferometry time series analysis: Probing the lithosphere rheological structure}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{112}(B03403), 1--18, \doi{10.1029/2006JB004344}.

\bibitem[{\textit{Cetin et~al.}(2014)\textit{Cetin, Cakir, Meghraoui, Ergintav, and Akoglu}}]{Cetin2014}
Cetin, E., Z.~Cakir, M.~Meghraoui, S.~Ergintav, and A.~M. Akoglu (2014), {Extent and distribution of aseismic slip on the Ismetpasa segment of the North Anatolian Fault (Turkey) from Persistent Scatterer InSAR}, \textit{Geochemistry, Geophysics, Geosystems}, \textit{15}, \doi{10.1002/2014GC005307}.

@@

\bibitem[{\textit{Crittenden}(1967)}]{Crittenden1967}
Crittenden, M. (1967), {Viscosity and Finite Strength of the Mantle as Determined from Water and Ice Loads}, \textit{Geophysical Journal of the Royal Astronomical Society}, 261--279, \doi{10.1111/j.1365-246X.1967.tb06243.x}.

\bibitem[{\textit{Davis et~al.}(2012)\textit{Davis, Wernicke, and Tamisiea}}]{Davis2012}
Davis, J.~L., B.~P. Wernicke, and M.~E. Tamisiea (2012), {On seasonal signals in geodetic time series}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{117}(B01403), 1--10, \doi{10.1029/2011JB008690}.

@@

\bibitem[{\textit{Freed et~al.}(2006)\textit{Freed, B{\"{u}}rgmann, Calais, Freymueller, and Hreinsd{\'{o}}ttir}}]{Freed2006a}
Freed, A.~M., R.~B{\"{u}}rgmann, E.~Calais, J.~Freymueller, and S.~Hreinsd{\'{o}}ttir (2006), {Implications of deformation following the 2002 Denali, Alaska, earthquake for postseismic relaxation processes and lithospheric rheology}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{111}{B01401}, 1--23, \doi{10.1029/2005JB003894}.

\bibitem[{\textit{Freed et~al.}(2007)\textit{Freed, B{\"{u}}rgmann, and Herring}}]{Freed2007a}
Freed, A.~M., R.~B{\"{u}}rgmann, and T.~Herring (2007), {Far-reaching transient motions after Mojave earthquakes require broad mantle flow beneath a strong crust}, \textit{Geophysical Research Letters}, \textit{34}(L19302), 1--5, \doi{10.1029/2007GL030959}.

\bibitem[{\textit{Gonzalez-Ortega et~al.}(2014)\textit{Gonzalez-Ortega, Fialko, Sandwell, Nava-pichardo, Fletcher, Gonzalez-garcia, Lipovsky, Floyd, and Funning}}]{Gonzalez-ortega2014}
Gonzalez-Ortega, A., Y.~Fialko, D.~Sandwell, F.~A. Nava-pichardo, J.~Fletcher, J.~Gonzalez-garcia, B.~Lipovsky, M.~Floyd, and G.~Funning (2014), {El Mayor-Cucapah (Mw7.2) earthquake: early near-field postseismic deformation from InSar and GPS observations}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{119}, 1482--1497, \doi{10.1002/2013JB010193}.

\bibitem[{\textit{Hauksson et~al.}(2011)\textit{Hauksson, Stock, Hutton, Yang, Vidal-Villegas, and Kanamori}}]{Hauksson2011}
Hauksson, E., J.~Stock, K.~Hutton, W.~Yang, J.~A. Vidal-Villegas, and H.~Kanamori (2011), {The 2010 Mw 7.2 El mayor-cucapah earthquake sequence, Baja California, Mexico and Southernmost California, USA: Active seismotectonics along the Mexican pacific margin}, \textit{Pure and Applied Geophysics}, \textit{168}, 1255--1277, \doi{10.1007/s00024-010-0209-7}.

\bibitem[{\textit{Hearn}(2003)}]{Hearn2003}
Hearn, E.~H. (2003), {What can GPS data tell us about the dynamics of post-seismic deformation}, \textit{Geophysical Journal International}, \textit{115}, 753--777, \doi{10.1111/j.1365-246X.2003.02030.x}.

\bibitem[{\textit{Hearn et~al.}(2009)\textit{Hearn, McClusky, Ergintav, and Reilinger}}]{Hearn2009} 
Hearn, E.~H., S.~McClusky, S.~Ergintav, and R.~E. Reilinger (2009), {Izmit earthquake postseismic deformation and dynamics of the North Anatolian Fault Zone}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{114}(B08405), 1--21, \doi{10.1029/2008JB006026}.

\bibitem[{\textit{Hetland}(2003)}]{Hetland2003}
Hetland, E.~A. (2003), {Postseismic relaxation across the Central Nevada Seismic Belt}, \textit{Journal of Geophysical Research}, \textit{108}(B8), 1--13, \doi{10.1029/2002JB002257}.

\bibitem[{\textit{Hetland and Zhang}(2014)}]{Hetland2014}
Hetland, E.~A., and G.~Zhang (2014), {Effect of shear zones on post-seismic deformation with application to the 1997 Mw 7.6 manyi earthquake}, \textit{Geophysical Journal International}, \textit{206}(2), 1--11, \doi{10.1093/gji/ggu127}.

@@

\bibitem[{\textit{Jacobs et~al.}(2002)\textit{Jacobs, Sandwell, Fialko, and Sichoix}}]{Jacobs2002}
Jacobs, A., D.~Sandwell, Y.~Fialko, and L.~Sichoix (2002), {The 1999 (Mw7.1) Hector Mine, California, Earthquake: Near-Field Postseismic Deformation from ERS Interferometry}, \textit{Bulletin of the Seismological Society of America}, \textit{92}(4), 1433--1442.

\bibitem[{\textit{Johnson and Segall}(2004)}]{Johnson2004}
Johnson, K.~M., and P.~Segall (2004), {Viscoelastic earthquake cycle models with deep stress-driven creep along the San Andreas fault system}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{109}(B10403), 1--19, \doi{10.1029/2004JB003096}.

@@

\bibitem[{\textit{J{\'{o}}nsson et~al.}(2003)\textit{J{\'{o}}nsson, Segall, Pedersen, and Bjornsson}}]{Jonsson2003}
J{\'{o}}nsson, S., P.~Segall, R.~Pedersen, and G.~Bjornsson (2003), {Post-earthquake ground movements correlated to pore-pressure transients}, \textit{Nature}, \textit{424}, 179--183, \doi{10.1038/nature01758.1.}

@@

\bibitem[{\textit{Kroll et~al.}(2013)\textit{Kroll, Cochran, Richards-Dinger, and Sumy}}]{Kroll2013}
Kroll, K.~A., E.~S. Cochran, K.~B. Richards-Dinger, and D.~F. Sumy (2013), {Aftershocks of the 2010 Mw 7.2 El Mayor-Cucapah earthquake reveal complex faulting in the Yuha Desert, California}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{118}, 6146--6164, \doi{10.1002/2013JB010529}.

\bibitem[{\textit{Lekic et~al.}(2011)\textit{Lekic, French, and Fischer}}]{Lekic2011}
Lekic, V., S.~W. French, and K.~M. Fischer (2011), {Lithospheric Thinning Beneath Rifted Regions of Southern California}, \textit{Science} \textit{334}, 783--787.

\bibitem[{\textit{Liu et~al.}(1976)\textit{Liu, Anderson, and Kanamori}}]{Liu1976}
Liu, H.-P., D.~L. Anderson, and H.~Kanamori (1976), {Velocity dispersion due to anelasticity; implications for seismology and mantle composition} \textit{Geophysical Journal of the Royal Astronomical Society}, \textit{47}, 41--58, \doi{10.1111/j.1365-246X.1976.tb01261.x}.

\bibitem[{\textit{Lundgren et~al.}(2009)\textit{Lundgren, Hetland, Liu, and Fielding}}]{Lundgren2009}
Lundgren, P., E.~A. Hetland, Z.~Liu, and E.~J. Fielding (2009), {Southern San Andreas-San Jacinto fault system slip rates estimated from earthquake cycle models constrained by GPS and interferometric synthetic aperture radar observations}, \textit{Journal of Geophysical Research: Solid Earth} \textit{114}(B02403), 1--18, \doi{10.1029/2008JB005996}.

\bibitem[{\textit{McGuire and Segall}(2003)}]{McGuire2003}
McGuire, J.~J., and P.~Segall (2003), {Imaging of aseismic fault slip transients recorded by dense geodetic networks}, \textit{Geophysical Journal International}, \textit{155}, 778--788, \doi{10.1111/j.1365-246X.2003.02022.x}.

\bibitem[{\textit{Meade and Hager}(2005)}]{Meade2005}
Meade, B.~J., and B.~H. Hager (2005), {Block models of crustal motion in southern California constrained by GPS measurements}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{110}(B03403), 1--19, \doi{10.1029/2004JB003209}.

\bibitem[{\textit{Murray and Segall}(2005)}]{Murray2005}
Murray, J.~R., and P.~Segall (2005), {Spatiotemporal evolution of a transient slip event on the San Andreas fault near Parkfield, California}, \textit{Journal of Geophysical Research: Solid Earth}, \textit{110}(B09407), 1--12, \doi{10.1029/2005JB003651}.

@@

\bibitem[{\textit{Pollitz et~al.}(2000)\textit{Pollitz, Peltzer, and B{\"{u}}rgmann}}]{Pollitz2000}
Pollitz, F.~F., G.~Peltzer, and R.~B{\"{u}}rgmann (2000), {Mobility of continental mantle: Evidence from postseismic geodetic observations following the 1992 Landers earthquake}, \textit{Journal of Geophysical Research}, \textit{105}(B4), 8035--8054, \doi{10.1029/1999JB900380}.
